Named Entity Recognition for Web Data Extraction

### 2019-06-16 tex/article.tex
General refactoring.

\author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
       {João Mateus de Freitas Veneroso$^A$ \and
        Berthier Ribeiro-Neto$^B$\\
	Universidade Federal de Minas Gerais$^{A,B}$ \\
	Google Engineering$^A$, Belo Horizonte - MG, Brazil}

@@

In this article, we compare different machine learning approaches to 
\gls{ner} on the web by evaluating their performance in the 
\gls{rne} task. With this purpose in mind, we introduce a novel \gls{ner} dataset 
with labeled entities, consisting of faculty directories from universities across the world. 
We compare the models in terms of their Precision, Recall, F-scores and their 
overall complexity. That is, even if a model has a slightly worse performance in terms of the
objective evaluation metrics in comparison to other approaches, it may still be useful if it 
is considerably simpler and faster to train.
The tested models were the \gls{hmm} up to third order, \gls{crf}, and a range of Deep Learning 
architectures based on Bidirectional \gls{lstm}. We also 
introduce the self-training strategy that can boost the performance 
of \gls{hmm}s in sequence labeling tasks for the web.

@@

The \gls{rne} task is a problem in \gls{wde} that
we proposed to solve with the application of machine learning methods of \gls{ner}.
This chapter presents the related research in the fields of \gls{wde} 
in Section~\ref{sec:wde} and \gls{ner} in Section~\ref{sec:ner}.

@@

\cite{Sarawagi2008} introduced a classification that segmented wrappers in
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of \gls{ner}, Relationship Extraction and \gls{wde}. 
The rule based methods encompass most of the previous models. While the statistical methods 
convert the extraction task into a token labeling task, solved with \gls{ner} 
and Relationship Extractions methods. Traditionally, these subtasks were solved with 
generative models based on \gls{hmm}s or discriminative models based on the 
Maximum Entropy principle, but recently these have been largely superseded by Deep Neural 
Networks. Different from automatic wrapper generators, statistical methods are suitable for
a large variety of tasks, especially when we want the system to handle cross website information 
extraction and plain text information extraction. That is why this class of methods is of 
special interest to our application. The progress of statistical models will be 
discussed in Section~\ref{sec:ner}.

Surveys by~\cite{Ferrara2014}, \cite{Schulz2016} and \cite{Varlamov2016} updated the 
previous surveys on Information Extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model~\cite{Krupl2005}, a data extraction system that produces 
a visualization of the webpage to exploit visual cues to identify records presented in a tabular form;
automatic wrapper adaptation~\cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM~\cite{Shi2015}, a method to mine
records from a single webpage by identifying similar data regions through DOM
tree analysis; and Knowledge Vault~\cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

@@

A statistical approach to unsupervised domain 
independent \gls{wde} was described by~\cite{Zhu2005}. The 2D CRF 
model takes a webpage segmented into data blocks and employs a two dimensional \gls{crf}
model to perform attribute labeling. The model was further improved 
in~\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also addressed by ObjectRunner~\cite{Abdessalem2010} and DIADEM~\cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

\gls{wde} methods have undoubtedly improved extraordinarily, but
as pointed by \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools. Also, many tools seem to rely excessively on heuristic methods.
The recent advancements in sequence taggers may provide more robust and flexible techniques
to address this problem.

@@

Traditionally, the \gls{ner} task was solved with generative models based on 
\gls{hmm}s. The first appearance of \gls{hmm}s in the
field of \gls{nlp} occurred in the mid-seventies and was
primarily focused on the problem of Speech Recognition. 
But in the late nineties, \gls{hmm}s also found important applications in \gls{ie}
and \gls{ner} as in the works by~\cite{Bikel1999}, 
\cite{Freitag1999}, and \cite{Freitag2000}.

@@

To our knowledge, the best NER system up to this date (considering the performance in the
{CoNLL-2003} dataset) is the bidirectional transformer model proposed by~\cite{Baevski2019} that uses
a stack of self-attention modules and ELMo embeddings. Table~\ref{tab:ner_model_comparison}
shows a comparison of the history of reported F1 scores in the English test set of the {CoNLL-2003} dataset
for the NER systems that were mentioned in this section. Each of the mentioned systems held the 
record for the task at a given time.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lc }
      \toprule
      Model & Test F1 \\
      \midrule
       \cite{Florian2003} ({CoNLL-2003} Winner)    & 88.76 \\
       \cite{Collobert2011}                        & 89.59 \\
       \cite{Huang2015}                            & 90.10 \\
       \cite{Lample2016}                           & 90.94 \\
       \cite{Ma2016}                               & 91.21 \\
       \cite{Peters2018}                           & 92.22 \\
       \cite{Devlin2018}                           & 92.80 \\
       \cite{Akbik2018}                            & 93.09 \\
       \cite{Baevski2019}                          & 93.50 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Model performances in the {CoNLL-2003} English test set.}
  \label{tab:ner_model_comparison}
\end{table}

@@

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is:
%
\begin{equation}
P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
\end{equation}
%
In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as with a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
Second, the probability of a word depends only on its assigned label. That is:
%
\begin{equation}
P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
\end{equation}
%
With these assumptions, 
the probability $ P(Y|X) $ can be calculated with the expression:
%
\begin{equation}
P(Y|X) \propto \prod_{i=k+1}^{n} P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)
\end{equation}
%
In a HMM, we need to estimate the following probabilities:
%
\begin{itemize}
  \item $ \hat{P}(x_i|y_i) $: the probability of word $ x_i $ given label $ y_i $.
  \item $ \hat{P}(y_i|y_{i-1}) $: the probability of going from label $ y_{i-1} $ to label $ y_i $.
\end{itemize}
%
These parameters can obtained with maximum likelihood estimation from the relative
frequencies of labels and words in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

@@

We propose the Self-Training strategy for \gls{hmm}s to incorporate knowledge about the HTML structure
and boost the quality of the model in sequence labeling tasks for the web.
Some \gls{wde} tasks, such as researcher name extraction, need extraction systems
that can handle different webpage structures without needing to resort to human supervision
between webpages. 
The problem is that there is not a lot of similarity between the HTML structure in different web pages.
For example, only because a named entity label occurs more often inside lists in a page, we cannot
assume that this will be the case on other web pages. 
Nonetheless, the HTML structure is not useless. Inside a single web page, the HTML tag is a good predictor
of the correct labels, because words with a similar HTML context tend to have similar labels. For example, words
that happen together inside a list are very likely to belong to the same category. 
Yet, this pattern cannot be generalized to other pages, because we cannot expect that every list will
be listing the same types of entities.

The Self-Training strategy for HMMs consists of using the predicted labels as a proxy for the
correct labels and estimating HTML feature probabilities for each webpage separately.
Consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
where all the feature are assumed to be independent, conditioned on $ y_i $. That is:
\begin{equation}
P(x_i|y_i) = P(f_{i,1}, f_{i,2}, ..., f_{i,k}|y_i) = \prod_{j=1}^k P(f_{i,j}|y_i)
\end{equation}
%
Assuming time invariance, we need to estimate parameters $ \hat{P}(f_{j}|y) $, 
relative to each possible assignment of $ y $.
The maximum likelihood estimators for these feature parameters can be obtained
from their relative frequencies in the corpus. That is:
%
\begin{equation}
\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, y=l)}
{\text{Count}(f_{j}=0, y=l) + \text{Count}(f_{j}=1, y=l)}
\label{eq:feature_mle}
\end{equation}
%
These estimators yield good experimental results for textual features such as the 
capitalization of a word, but for the reasons already discussed, it does not work
well with HTML features, such as the current HTML tag. To make better use of the
HTML features, consider a set $ F_T $ textual features unrelated to the HTML structure
and a set $ F_H $ of HTML features related to the HTML structure.
We can use a \gls{hmm} trained exclusively with the first set of features $ F_T $
to predict the labels of an unlabeled webpage. With the predicted labels $ \tilde{y} $, we calculate
the HTML feature probabilities $ \hat{P}(f_{j}=1|\tilde{y}=l) $ using the feature counts from
that webpage alone. Next, we incorporate the estimators for the HTML feature probabilities 
in the original \gls{hmm} and predict the final labels with the whole set of features 
{$ F_T~\cup~F_H $}. This needs to be done separately for every webpage and
the process can be repeated multiple times. If the predictions are becoming more accurate with
each iteration, then the estimates for the HTML feature probabilities are also likely to improve. 
This self-training strategy showed good experimental results in the \gls{rne} task. Stated
simply, it can be divided into the following steps:
%
\begin{itemize}
\item Train the HMM without any HTML features.
\item Compute labels for a website with the trained HMM.
\item Use the computed labels as a proxy for the actual labels in the 
website and estimate HTML feature frequencies for this website alone.
\item Recompute the labels now using the HTML feature probabilities.
\end{itemize}
%
This strategy could be used with any sequence tagger, however retraining a classifier 
with new features in every webpage can become prohibitively expensive in the case of 
CRFs or Neural Networks. Contrastingly, in \gls{hmm}s, retraining the HTML features is fast, 
because we assume feature independence and the maximum likelihood estimator can be obtained 
with a simple closed form expression.

@@

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
it was first introduced by Lafferty \cite{Lafferty2001}. The model can be described by a 
distribution $ P(Y|X) $ that takes the form:
%
\begin{equation}
P(Y|X) = \frac{1}{Z(x)} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, X) \right)
\end{equation}
%
where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
are feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:
%
\begin{equation}
Z(x) = \sum_{Y} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x) \right)
\end{equation}
%
which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm.

@@

Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
neural networks, RNNs can retain information in their internal state, making them more 
suitable for processing sequences, and consequently for solving text related tasks. 
Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
timesteps. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}
%
At each timestep, the neural network computes a hidden state $ h_t $ using an input 
vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
timestep. A common definition for an RNN cell is given by the equations:
%
\begin{align*}
h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
y_t &= softmax(W_y h_t) &
\end{align*}
%
Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
and retaining long term dependencies through their internal state $ h_t $. However, in practice,
it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
have been popularized since then.

@@

Huang et al. \shortcite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
in the neural sequence model is that the labels are jointly decoded for a whole sentence 
instead of being predicted individually. Another possibility would be to use a beam search
decoder to find an optimal sequence of labels. Predicted tags should be highly correlated 
in a named entity recognition task, so it is desirable to predict sequences conjointly.
The BI-LSTM-CRF is described in Figure~\ref{fig:bi_lstm_crf}.

@@

This architecture achieved an F1 score of 90.10 on the English data from the CoNLL-2003 
NER shared task \cite{KimSang2003}, in contrast to 85.17 for a bidirectional LSTM without 
a CRF layer. 
In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
hidden states, no peepholes and input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

@@

The convolutional neural network receives character embeddings as inputs. The character 
representations generated by the CNN are combined with word level representations 
and fed to the BI-LSTM-CRF described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained an F1 score of 91.21 in the CoNLL2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 30 filters and a window size of three characters on top of the LSTM-CRF 
architecture. The character embeddings fed to the CNN have 30 dimensions that are randomly 
initialized.

@@

This character representation is also combined with a word 
representation and fed to a BI-LSTM-CRF network. 
The forward state is expected to be a better representation of the suffix of 
a token, and the backward state is expected to be a better representation of 
the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section~\ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent 
suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional 
LSTM with 25 hidden states, producing character representations of 
size 50. The character embeddings have 30 dimensions that are randomly initialized.

@@

In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 300-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.

@@

We collected 145 Computer Science and Engineering faculty pages from 42 different countries in
multiple languages, although the English version was preferred when it was available.
We gathered faculty webpages in proportion to
the number of universities in each country\footnote{A detailed list of universities can
be found in https://univ.cc/world.php}. 
The dataset size was limited to a number of pages that could be viably labeled manually and
that could still represent many different countries. 
Also, university pages that contained 
corrupt HTML or JavaScript code that performed lazy loading of data records were
not included in this dataset.

@@

Most webpages in this dataset are faculty directories with informative
text in small passages, however long prose is not absent. 
Size and structure varies wildly, therefore some documents 
may contain up to a few hundred names whereas other documents may contain 
only a dozen names. This difference in document size and characteristics 
may be problematic when comparing different extraction systems, because a system 
that performs well on some types of pages may perform poorly in other types.
To avoid this problem, we tried to keep the proportion between the number of tokens
and the number of documents roughly the same for all data files.

@@

% \cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually,

>>>>

\author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
       {João Mateus de Freitas Veneroso$^A$ \and
        Berthier Ribeiro-Neto$^B$\\
	Universidade Federal de Minas Gerais$^{A,B}$ \\
	Google Engineering$^B$, Belo Horizonte - MG, Brazil}

@@

In this article, we compare different machine learning approaches to 
\gls{ner} on the web by evaluating their performance in the 
\gls{rne} task. With this purpose in mind, we introduce a novel \gls{ner} dataset 
with labeled entities, consisting of faculty directories from universities across the world,
the RNE dataset~\footnote{
The dataset is available in https://github.com/jmfveneroso/ner-on-html.
}.
We compare the models in terms of their Precision, Recall, F-scores and their 
overall complexity. That is, even if a model has a slightly worse performance in terms of the
objective evaluation metrics in comparison to other approaches, it may still be useful if it 
is considerably simpler and faster to train.
The tested models were the \gls{hmm} up to third order, \gls{crf}, and a range of Deep Learning 
architectures based on Bidirectional \gls{lstm}. We also 
introduce the self-training strategy that can boost the performance 
of \gls{hmm}s in sequence labeling tasks for the web.

@@

The \gls{rne} task is a problem in \gls{wde} that
we proposed to solve with the application of machine learning methods of \gls{ner}.
This section presents the related research in the fields of \gls{wde} 
in Section~\ref{sec:wde} and \gls{ner} in Section~\ref{sec:ner}.

@@

Sarawagi~\shortcite{Sarawagi2008} introduced a classification that segmented wrappers in
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of \gls{ner}, Relationship Extraction and \gls{wde}. 
The rule based methods encompass most of the previous models. While the statistical methods 
convert the extraction task into a token labeling task, solved with \gls{ner} 
and Relationship Extractions methods. Traditionally, these subtasks were solved with 
generative models based on \gls{hmm}s or discriminative models based on the 
Maximum Entropy principle, but recently these have been largely superseded by Deep Neural 
Networks. Different from automatic wrapper generators, statistical methods are suitable for
a large variety of tasks, especially when we want the system to handle cross website information 
extraction and plain text information extraction. That is why this class of methods is of 
special interest to our application. The progress of statistical models will be 
discussed in Section~\ref{sec:ner}.

Recent surveys by Ferrara, De Meo, Fiumara and Baumgartner~\shortcite{Ferrara2014}, 
Schulz, Lassig and Gaedke~\shortcite{Schulz2016} and
Varlamov and Turdakov~\shortcite{Varlamov2016}
updated the previous surveys on Information Extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model~\cite{Krupl2005}, a data extraction system that produces 
a visualization of the webpage to exploit visual cues to identify records presented in a tabular form;
automatic wrapper adaptation~\cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM~\cite{Shi2015}, a method to mine
records from a single webpage by identifying similar data regions through DOM
tree analysis; and Knowledge Vault~\cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

@@

A statistical approach to unsupervised domain 
independent \gls{wde} was described by Zhu, Nie, Wen, Zhang, and Ma~\shortcite{Zhu2005}. The 2D CRF 
model takes a webpage segmented into data blocks and employs a two dimensional \gls{crf}
model to perform attribute labeling. The model was further improved~\cite{Zhu2006} to model 
record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also addressed by ObjectRunner~\cite{Abdessalem2010} and DIADEM~\cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

\gls{wde} methods have undoubtedly improved extraordinarily, but
as pointed by Schulz, Lassig and Gaedke~\shortcite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools. Also, many tools seem to rely excessively on heuristic methods.
The recent advancements in sequence taggers may provide more robust and flexible techniques
to address this problem.

@@

Traditionally, the \gls{ner} task was solved with generative models based on 
\gls{hmm}s. The first appearance of \gls{hmm}s in the
field of \gls{nlp} occurred in the mid-seventies and was
primarily focused on the problem of Speech Recognition. 
But in the late nineties, \gls{hmm}s also found important applications in \gls{ie}
and \gls{ner} as in the works by Bikel, Schwartz and Weischedel~\shortcite{Bikel1999}, 
Freitag and Mccallum~\shortcite{Freitag1999}, 
and Freitag and Mccallum~\shortcite{Freitag2000}.

@@

To our knowledge, the best NER system up to this date (considering the performance in the
{CoNLL-2003} dataset) is the bidirectional transformer model proposed by Baevski, Edunov, Liu, Zettlemoyer and Auli~\shortcite{Baevski2019} that uses
a stack of self-attention modules and ELMo embeddings. Table~\ref{tab:ner_model_comparison}
shows a comparison of the history of reported F1 scores in the English test set of the {CoNLL-2003} dataset
for the NER systems that were mentioned in this section. Each of the mentioned systems held the 
record for the task at a given time.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lc }
      \toprule
      Model & Test F1 \\
      \midrule
      Florian, Ittycheriah, Jing and Zhang 2003 (CoNLL-2003 Winner)            & 88.76 \\
      Collobert, Weston, Bottou, Karlen, Kavukcuoglu, and Kuksa 2011           & 89.59 \\
      Huang, Xu and Yu 2015                                                    & 90.10 \\
      Lample, Ballesteros, Subramanian, Kawakami and Dyer 2016                 & 90.94 \\
      Ma and Hovy 2016                                                         & 91.21 \\
      Peters, Neumann, Iyyer, Gardner, Clark, Lee and Zettlemoyer 2018         & 92.22 \\
      Devlin, Chang, Lee, and Toutanova 2018                                   & 92.80 \\
      Akbik, Blythe and Vollgraf 2018                                          & 93.09 \\
      Baevski, Edunov, Liu, Zettlemoyer and Auli 2019                          & 93.50 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Model performances in the {CoNLL-2003} English test set.}
  \label{tab:ner_model_comparison}
\end{table}

@@

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is:
%
\begin{equation}
P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
\end{equation}
%
In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as with a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
Second, the probability of a word depends only on its assigned label. That is:
%
\begin{equation}
P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
\end{equation}
%
With these assumptions, 
the probability $ P(Y|X) $ can be calculated with the expression:
%
\begin{equation}
P(Y|X) \propto \prod_{i=k+1}^{n} P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)
\end{equation}
%
In a HMM, we need to estimate the following probabilities:
%
\begin{itemize}
  \item $ \hat{P}(x_i|y_i) $: the probability of word $ x_i $ given label $ y_i $.
  \item $ \hat{P}(y_i|y_{i-1}) $: the probability of going from label $ y_{i-1} $ to label $ y_i $.
\end{itemize}
%
These parameters can be obtained with maximum likelihood estimation from the relative
frequencies of labels and words in the corpus. However, tokens that do not happen in the
training set will have null probability, what is problematic because named entities often
contain unknown tokens. To counter this problem, we used additive smoothing in the 
emission probability estimates.
The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

@@

We propose the Self-Training strategy for \gls{hmm}s to incorporate knowledge about the HTML structure
and boost the quality of the model in sequence labeling tasks for the web.
Some \gls{wde} tasks, such as researcher name extraction, need extraction systems
that can handle different webpage structures without needing to resort to human supervision
between webpages. 
The problem is that there is not a lot of similarity between the HTML structure in different web pages.
For example, only because a named entity label occurs more often inside lists in a page, we cannot
assume that this will be the case in other web pages. 
Nonetheless, the HTML structure is not useless. Inside a single web page, the HTML tag is a good predictor
of the correct labels, because words with a similar HTML context tend to have similar labels. For example, words
that happen together inside a list are very likely to belong to the same category.

The Self-Training strategy for HMMs consists of using the predicted labels as a proxy for the
correct labels and estimating HTML feature probabilities for each webpage separately.
Consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
where all the feature are assumed to be independent, conditioned on $ y_i $. That is:
\begin{equation}
P(x_i|y_i) = P(f_{i,1}, f_{i,2}, ..., f_{i,k}|y_i) = \prod_{j=1}^k P(f_{i,j}|y_i)
\end{equation}
%
Assuming time invariance, we need to estimate parameters $ \hat{P}(f_{j}|y) $, 
relative to each feature and assignment of $ y $.
The maximum likelihood estimators for these feature parameters can be obtained
from their relative frequencies in the corpus. That is:
%
\begin{equation}
\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, y=l)}
{\text{Count}(f_{j}=0, y=l) + \text{Count}(f_{j}=1, y=l)}
\label{eq:feature_mle}
\end{equation}
%
These estimators yield good experimental results for textual features such as the 
capitalization of a word, but for the reasons already discussed, they do not work
well with HTML features, such as the current HTML tag. To make better use of the
HTML features, consider a set $ F_T $ features unrelated to the HTML structure
and a set $ F_H $ of features related to the HTML structure.
We can use a \gls{hmm} trained exclusively with the first set of features $ F_T $
to predict the labels of an unlabeled webpage. With the predicted labels $ \tilde{y} $, we calculate
the HTML feature probabilities $ \hat{P}(f_{j}=1|\tilde{y}=l) $ using the feature counts from
that webpage alone. Next, we incorporate the estimators for the HTML feature probabilities 
in the original \gls{hmm} and predict the final labels with the whole set of features 
{$ F_T~\cup~F_H $}. This needs to be done separately for every webpage and
the process can be repeated multiple times. If the predictions are becoming more accurate with
each iteration, then the estimates for the HTML feature probabilities are also likely to improve. 
This self-training strategy showed good experimental results in the \gls{rne} task. Stated
simply, it can be divided into the following steps:
%
\begin{itemize}
\item Train the HMM without any HTML features.
\item Compute labels for a website with the trained HMM.
\item Use the computed labels as a proxy for the actual labels in the 
website and estimate HTML feature frequencies for this website alone.
\item Recompute the labels now using the HTML feature probabilities.
\end{itemize}
%
This strategy could be used with any sequence tagger, however retraining a classifier 
with new features in every webpage can become prohibitively expensive in the case of 
CRFs or Neural Networks. Contrastingly, in \gls{hmm}s, retraining the HTML features is fast, 
because we assume feature independence and the maximum likelihood estimator can be obtained 
with a simple closed form expression.

@@

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
it was first introduced by Lafferty \cite{Lafferty2001}. The model can be described by a 
distribution $ P(Y|X) $ that takes the form:
%
\begin{equation}
P(Y|X) = \frac{1}{Z(x)} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, X) \right)
\end{equation}
%
where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
are the feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:
%
\begin{equation}
Z(x) = \sum_{Y} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x) \right)
\end{equation}
%
which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm.

@@

Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
neural networks, RNNs can retain information in their internal state, making them more 
suitable for processing sequences, and consequently for solving text related tasks. 
Figure~\ref{fig:rnn_network} describes a RNN for sequence labeling unrolled through multiple 
timesteps. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}
%
At each timestep, the neural network computes a hidden state $ h_t $ using an input 
vector $ x_t $ and the previous hidden state $ h_{t-1} $ that retains information from past 
iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
timestep. A common definition for a RNN cell is given by the equations:
%
\begin{align*}
h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
y_t &= softmax(W_y h_t) &
\end{align*}
%
Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
and retaining long term dependencies through their internal state $ h_t $. However, in practice,
it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
have been popularized since then.

@@

Huang et al. \shortcite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
in the neural sequence model is that the labels are jointly decoded for a whole sentence 
instead of being predicted individually. 
Predicted tags should be highly correlated 
in a named entity recognition task, so it is desirable to predict sequences conjointly.
The BI-LSTM-CRF is described in Figure~\ref{fig:bi_lstm_crf}.

@@

This architecture achieved a F1 score of 90.10 on the English data from the CoNLL-2003 
NER shared task \cite{KimSang2003}, in contrast to 85.17 for a bidirectional LSTM without 
a CRF layer. 
In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
hidden states, no peepholes and input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

@@

The \gls{cnn} receives character embeddings as inputs and extracts
morphological features by sliding one dimensional filters over the sequence of characters 
and collapsing the filter outputs with a global max pooling layer, producing character
representations with a size determined by the number of filters. 
This means, that when a filter gets a good match at any position in the sequence, the 
max pooling layer output relative to that filter will be triggered, therefore this type of 
character representation detects position invariant morphological features. For example,
the word "finger" would trigger a filter for "ing" the same way the word "writing" would
trigger this filter. The character 
representations generated by the CNN are combined with word level representations 
and fed to the BI-LSTM-CRF described in section \ref{sssec:lstm_crf}.
This architecture can learn morphological features that are very
useful in the NER task, since similar named entities often present morphological similarities. 
This architecture obtained a F1 score of 91.21 in the CoNLL-2003 dataset. In our experiments, 
the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
neural network with 50 filters and a window size of three characters on top of the LSTM-CRF 
architecture. The character embeddings fed to the CNN have 50 dimensions that are randomly 
initialized.

@@

This character representation is also combined with a word 
representation and fed to a BI-LSTM-CRF network. 
The forward state is expected to be a better representation of the suffix of 
a token, and the backward state is expected to be a better representation of 
the prefix of a token. This differentiates the architecture
from the CNN based approach described in Section~\ref{sssec:lstm_crf_cnn}, because CNN filters 
discover positional invariant features, while LSTMs can better represent 
suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional 
LSTM with 25 hidden states, producing character representations of 
size 50. The character embeddings have 50 dimensions that are randomly initialized.

@@

In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 20 epochs with batch size 10,
learning rate 0.001, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 300-dimensional word embeddings \cite{Pennington2014} that were not fine tuned during training.

@@

We collected 145 Computer Science and Engineering faculty pages from 42 different countries in
multiple languages, although the English version was preferred when it was available.
We gathered faculty webpages in proportion to
the number of universities in each country\footnote{A detailed list of universities can
be found in https://univ.cc/world.php}. 
University pages that contained 
corrupt HTML or JavaScript code that performed lazy loading of data records were
not included in this dataset.

@@

Most webpages in this dataset are faculty directories with informative
text in small passages, however long prose is not absent. 
Size and structure varies wildly, therefore some documents 
may contain up to a few hundred names whereas other documents may contain 
only a dozen names.

@@
